\documentclass{tufte-handout}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage{booktabs}
\usepackage{microtype}

\pagestyle{empty}


\title{Stable Matching Report}
\author{Bryndís Eva Erlingsdóttir, David Godzsak, Erida Nurçe, Jorgel Keci, Karen Janani Salazar Lopez, Theis Trøjborg Jensen}

\begin{document}
  \maketitle

  \section{Results}

  Our implementation produces the expected results on all of the input-output file pairs. We tested all of them through the shell scripting provided.
    

  \section{Implementation details}
  
   Both men and women preferences are stored in 2-Dimensional Integer arrays to make search time O(1). With the same purpose in mind, we      have used Arrays throughout the whole implementation.
   We are parsing the input from the file and spliting them on men preferences and women preferences.
   
   
   We then created an array named ranking to keep track of the women preferences in order.
   
   We used Stack to keep track of unmatched men.
   In the current array we are storing the matches indexed by the women ID and simultaneously in result array we are storing the same        matches but this time indexed by the men's ID.
   
  We can check find a free man who has not proposed to every woman in time $[\ldots]$,
  because we store $[\ldots]$.

  With these data structures, our implementation runs in time $O(n\log n)$  \sidenote{Replace with your actual running time.}
  on inputs with $n$ men and $n$ women.


\end{document}
